Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on results

\begin{table}[h!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
    & Timeout/OME & 13 \\
    & Not Implemented & 21 \\
    & Non-Standard Element & \Fix{132} \\
    & Unknown & \Fix{-} \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 9 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[h!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 177 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}
